On the effects of partying on next-day sports performance

### 2017-05-27 writing/draft.tex
Init commit.

\section{Previous Research}

\section{Materials and Methods}
\subsection{Data}
\subsubsection{Lines data} We obtained data from \href{http://www.covers.com/sports/NBA/matchups?selectedDate=2011-1-01}{Covers.com}, which records the outcome of each game alongside the line set by a betting house.

@@

>>>>

Citations toward anecdotal. % The ``JR Smith'' effect.

\section{Previous Research}
Studies on effects of alcohol on sports performance in a controlled setting.

\section{Materials and Methods}
Determining when players partied. One might consider to look at Twitter data
and or night clubs per city.

Insights: major party cities are LA and NY, and athletes party is well correlated with musicians. This led to two separate definitions of party. Our most basic analysis was to consider performance 
the day after visiting LA or NY.
We also considered the number of musical establishments per city.

\paragraph{Logic for using spread data}
The logic for using spread data: it controls for a lot, but we don't know exactly
what it controls for.

\subsection{Data}
\subsubsection{Lines data} We obtained data from \href{http://www.covers.com/sports/NBA/matchups?selectedDate=2011-1-01}{Covers.com}, which records the outcome of each game alongside the line set by a betting house.

@@

\subsection{Extending the research}
We can also validate where points are lost in MLB in a similar way.

\subsection{Betting performance}
